---
title: "Evaluación 1"
output: html_notebook
---

# Análisis de datos en R para antropología

### Paquetes a utilizar

```{r, echo=TRUE, include=TRUE}
library(tidyverse)
library(dslabs)
library(HistData)
```

### R basico: Objetos

-   Crea un vector númerico de un largo de 10 y crea un vector de caracteres de largo 10 (pueden ser letras)

    ```{r}
    vector_1<- 1
      
    vector_2 <- 1

    ```

-   Crea una matriz

    ```{r}
    1
    ```

-   Crea un dataframe

    ```{r}
    1
    ```

¿Cuál es la principal diferencia entre una matriz (matrix) y un dataframe?

> Respuesta aquí

------------------------------------------------------------------------

### Procesos

-   Crea un vector númerico de un largo de 10 y crea un vector de caracteres de largo 10 (pueden ser letras)

    ```{r}
    vector_1<- 1
      
    vector_2 <- 1

    ```

-   Crea una matriz

    ```{r}
    1
    ```

-   Crea un dataframe

    ```{r}
    1
    ```

¿Cuál es la principal diferencia entre una matriz (matrix) y un dataframe?

> Respuesta aquí

------------------------------------------------------------------------

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

------------------------------------------------------------------------

```{r}
sessionInfo()
```
